%-------------------------
% Resume in Latex
% Author : Chen Xiang
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontspec}
\usepackage{xeCJK}
\setCJKmainfont{Heiti TC}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xstring}
\usepackage{ifthen}
\usepackage{fontawesome5}
\usepackage[normalem]{ulem} % For customizable underlines
% \input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage[sfdefault]{carlito}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

% Phone number display control (default: true)
\providecommand{\showphone}{true}
\providecommand{\phonenumber}{+852 0000-0000}

%-------------------------
% Custom commands

% Custom thin underline command
\newcommand{\thinunderline}[1]{\uline{#1}}
% Adjust underline thickness (0.4pt is thinner than default)
\renewcommand{\ULthickness}{0.2pt}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Chen Xiang } \textbf{\huge \scshape 陳想}\\ \vspace{3pt}
    \small
    \ifthenelse{\equal{\showphone}{true}}{\raisebox{-1pt}{\faPhone} \space \phonenumber \space $|$}{}
    \raisebox{-1pt}{\faEnvelope} \space \href{mailto:xiiang.ch@gmail.com}{\thinunderline{xiiang.ch@gmail.com}} $|$
    \raisebox{-1pt}{\faGlobe} \space \href{https://cxiang.site}{\thinunderline{cxiang.site}} $|$
    \raisebox{-1pt}{\faGithub} \space \href{https://github.com/Xiang-CH}{\thinunderline{github.com/Xiang-CH}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://hku.hk/}{The University of Hong Kong}}{Hong Kong}
      {Master of Science in Computer Science}{Sep. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Quantum Computing, Data Mining, Algorithmic Trading, Unmanned Systems}
      \resumeItemListEnd
      \vspace{-5pt}
      \resumeSubSubheading
      {Bachelor of Engineering in Computer Science}{Sep. 2021 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{First Class Honours, Dean's Honours List (2021-2022)}
        \resumeItem{Relevant Coursework: Machine Learning, Computer Vision, Operating Systems, Object-Oriented Programming, Data Science, Software Engineering, Algorithm Design, Databases, Network Communications, Natural Language Processing, Deep Learning}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.linkedin.com/school/universityofhongkong}{The University of Hong Kong}}{Hong Kong}
      {Research Assistant II}{Jul 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developing Legal AI tools in collaboration with the Law and Technology Centre, HKU, to support teaching and learning initiatives at HKU Law School.}
        \resumeItem{Processed and structured raw Hong Kong legal documents for context engineering, building a relational semantic database to enable efficient information retrieval in Agentic Retrieval-Augmented Large Language Model legal applications.}
      \resumeItemListEnd
      
   \resumeSubSubheading
    {Student Research Assistant}{Jun 2023 -- May 2024, Sep 2024 -- Jul 2025}
    \resumeItemListStart
       \resumeItem{Designed and led multiple hands-on AI workshops at the Innovation Wing, HKU, covering topics such as building \href{https://github.com/Xiang-CH/Innochat-Template}{\thinunderline{custom chatbots}} using Azure services and developing multi-modal Retrieval-Augmented Generation (RAG) applications with layout detection for document understanding.}
      \resumeItem{Collaborated on student-led AI projects, including \href{https://clic-search.vercel.app/}{\thinunderline{CLIC-Search}}: a semantic search engine for the Community Legal Information Center, and \href{https://aiha.vercel.app/}{\thinunderline{AI Historian Assistant}}: a multi-modal history research assistant.}
    \resumeItemListEnd


    \resumeSubheading
      {\href{https://www.linkedin.com/company/iflytekcoltd.}{iFLYTEK Co., Ltd.}}{Shenzhen}
      {Assistant Software Development Engineer}{Jun 2024 -- Aug 2024}
      \resumeItemListStart
        \resumeItem{Contributed to the agile development of AI English-speaking tutor and AI picture book companion LLM solutions within the education product line.}
        \resumeItem{Developed and maintained application pipelines using \emph{Node-RED} to support customized feature requirements.}
        \resumeItem{Automated data engineering workflows for model fine-tuning with \emph{Python} scripts and optimized prompt tuning processes using tools such as \emph{promptfoo}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://hk-legal-ai.vercel.app/search}{\thinunderline{CLIC-Chats}}} $|$ \emph{Next.js, Prisma, MS-SQL, Azure, LLM, RAG}}{Jul 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack AI agent web application for Hong Kong legal document Q\&A using \emph{Next.js} and \emph{Prisma}.}
            \resumeItem{Processed and extracted information from raw Hong Kong legal documents (legislation, judgments, and articles) by parsing and cleaning diverse data sources, and built a relational database in \emph{MS-SQL}.}
            \resumeItem{Created a hybrid search index (vector + keyword) on \emph{Azure AI Search} by semantically chunking and embedding legal documents.}
            \resumeItem{Implemented a Retrieval-Augmented Generation (RAG) pipeline featuring hybrid retrieval, relationship extraction, and reranking to improve document relevance and generate accurate responses using Large Language Models (LLMs).}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://cucampus.one/}{\thinunderline{CU-Campus}}} $|$ \emph{React, React Router, Tailwind CSS, Vite, i18n}}{May 2024 -- Oct 2024}
          \resumeItemListStart
            \resumeItem{CU Campus is a course review and calendar scheduling platform for CUHK students, seamlessly integrating multiple campus utilities to create a comprehensive one-stop information portal.}
            \resumeItem{Actively participated in UX design, feature planning, and iterative development cycles.}
            \resumeItem{Engineered the frontend using \emph{React}, tri-lingual localization with \emph{i18n}, and integrated with backend RESTful APIs.}
          \resumeItemListEnd

      \resumeProjectHeading
          {See more at: \href{https://cxiang.site/project}{\textbf{\thinunderline{cxiang.site/project}}}}{}
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Python, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: Node.js, Next.js, Flask, FastAPI, Tailwind CSS, Prisma, Vue.js, Chrome Extensions} \\
     \textbf{Databases}{: MS-SQL, MongoDB, PostgreSQL, MySQL, ChromaDB} \\
     \textbf{Developer Tools}{: Git, Docker, Linux, Azure, AWS, Postman, OpenAI API, Vercel, AI SDK, Clerk, Node-RED, Dify, n8n} \\
     \textbf{Libraries}{: React, Pandas, NumPy, Matplotlib, PyTorch, Scikit-learn, LangChain, BeautifulSoup, Selenium}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
